### 2023-08-28 main.tex
fix 3
Fix3

\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})

@@

\begin{align}
Q_{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N\\
Q_{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1\\
Q_{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
\left[Q_{2L},H^{''}\right]=Q_{2L}H^{''}-H^{''}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
\begin{equation}
Q_{2L}^{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
\end{equation}
that is 
%\begin{equation}
%\begin{split}
%Q_{2L}^{0}&=N(I^{tot}+e_{NN}^{tot})+e_{NN}^{tot}(2e_{NN}^{tot}+I^{tot})-\sum_{j=1}^{N-1}e_{jj}^{tot}-2N\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{k=1}^{N-1}\left\{e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{j=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right\}
%\end{split}
%\end{equation}
\begin{equation}\label{Q0Exp}
\begin{split}
Q_{2L}^{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
\end{split}
\end{equation}
%\begin{equation}	
%\begin{split}
%Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
%&=N+2e_{11}^{tot}(e_{11}^{tot}+1)+(N+2)(e_{11}^{tot}-L)+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
%\end{split}
%\end{equation} 
We also introduce 
\begin{equation}
\mathcal{Q}_{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{equation}
therefore we can write 
\begin{equation}
Q_{2L}=Q_{2L}^{0}+\mathcal{Q}_{2L}
\end{equation}
Observe that $Q_{2L}$ and $Q_{2L}^{0}$ are isospectral. \\
%  It has the property that commute with the equilibrium Hamiltonian.

@@

\section{Conserved charges form of W}

@@

Following the result in the simpler $gl(2)$ case, we aim to generalize it to higher rank chains. 

>>>>

\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}

@@

\begin{align}
Q_{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N\\
Q_{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1\\
Q_{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
\left[Q_{2L},H^{''}\right]=Q_{2L}H^{''}-H^{''}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
\begin{equation}
Q_{2L}^{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
\end{equation}
that is 
%\begin{equation}
%\begin{split}
%Q_{2L}^{0}&=N(I^{tot}+e_{NN}^{tot})+e_{NN}^{tot}(2e_{NN}^{tot}+I^{tot})-\sum_{j=1}^{N-1}e_{jj}^{tot}-2N\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{k=1}^{N-1}\left\{e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{j=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right\}
%\end{split}
%\end{equation}
\begin{equation}\label{Q0Exp}
\begin{split}
Q_{2L}^{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
\end{split}
\end{equation}
%\begin{equation}	
%\begin{split}
%Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
%&=N+2e_{11}^{tot}(e_{11}^{tot}+1)+(N+2)(e_{11}^{tot}-L)+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
%\end{split}
%\end{equation} 
We also introduce 
\begin{equation}\label{Q-nonDiag}
\mathcal{Q}_{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}=\sum_{i=1}^{N-1}2\Delta_{i}B_{i}^{2L-1}
\end{equation}
where $\Delta_{i}=(\alpha_{i}-\beta_{i})$. 
Therefore we can write 
\begin{equation}
Q_{2L}=Q_{2L}^{0}+\mathcal{Q}_{2L}
\end{equation}
Observe that $Q_{2L}$ and $Q_{2L}^{0}$ are isospectral. \\
%  It has the property that commute with the equilibrium Hamiltonian.

@@

\subsection{Conserved charges form of W}

@@

Following the result in the simpler $gl(2)$ case, we aim to generalize it to higher rank chains. Repeating the computations we find that 
Using the fact that $\left[H^{'},Q^{2L}\right]=0$ we can determine the matrix $W$ in function of the first non-trivial conserved charge $Q^{2L}$ as
		W&= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}-\mathcal{Q}_{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
 Recalling the expression of $\mathcal{Q}^{2L}$ given in \eqref{Q-nonDiag} we write the multi-variable power expansion with respect to $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$. We obtain that, using the multi-variate version of \eqref{veryUsefulSeries},
		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)
		\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
Here $SYM$ is the following transformation. Introduce, the following $i_{j}$ with $j=1,\ldots,k_{1}+\ldots+k_{N}$ indices, such that 
		&i_{1}=\ldots=i_{k_{1}}=1\\
	&	i_{k_{1}+1}=\ldots=i_{k_{1}+k_{2}}=2\\
		&\vdots\\
		&i_{k_{1}+\ldots+k_{N-2}+1}=\ldots=i_{k_{1}+\ldots+k_{N-1}}=N-1
By denoting with 
	A_{i_{j}}=\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{i_{j}}^{2L-1}\right\}
then 
&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)\\&:=\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{1}+\ldots+k_{N-1}})}
where $Sym$ is the symmetric group. 
We further observe that in the limit for $\epsilon\to 0$ the quantity 
	\lim_{\epsilon\to 0}	\epsilon\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle=|\Psi_{\bm{m}}^{0}\rangle
therefore we have that 
		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
		|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
